Comparing R packages for calculation of persistent homology

### 2020-03-19 tdabench-paper/tdabench.Rmd
removed a comment that was already addressed
removed 1 comment after discussing

<!--SHOULD BE IN METHODS
The GUDHI library provided functionality to calculate persistent homology with Rips and Alpha complexes. 
Therefore, we only used the GUDHI library to compare performance between Rips and Alpha complexes.-->

Even with a constant feature dimension, the underlying data dimension could play a role in runtime of persistent homology calculation.
Figure \ref{fig:ann} compares handling of this issue by the Vietoris-Rips complex and the alpha complex.
Since GUDHI is the only library implementing functionality with an alpha complex, we compare its implementations of the Vietoris-Rips and alpha complices.
Due to computational limitations, an alpha complex could not be calculated for any point clouds with data dimension exceeding 3.
Two notable aspects of Figure \ref{fig:ann} stand out.
First, the alpha complex calculation clearly runs faster than the Vietoris-Rips complex calculation, a trend that becomes clearer as point cloud size increases.
Second, although the Vietoris-Rips complex calculation runtime appears to be independent of underlying data dimension, alpha complex calculation is dependent on it.
Figure \ref{fig:ann} shows a subtle difference between data dimensions 2 and 3 as point cloud size increases.
Although unconcerning for a data dimension up to 3, failure to run any alpha complex calculations with a data dimension of 4 could be cause for concern.
<!--SHOULD BE IN DISCUSSION
This is understandable as Alpha complex theoretical complexity increases exponentially for increasing point cloud dimension.
Changes in computational performance from changing point cloud dimension is one major difference between calculation of Rips and Alpha complexes.-->

>>>>

Even with a constant feature dimension, the underlying data dimension could play a role in runtime of persistent homology calculation.
Figure \ref{fig:ann} compares handling of this issue by the Vietoris-Rips complex and the alpha complex.
Since GUDHI is the only library implementing functionality with an alpha complex, we compare its implementations of the Vietoris-Rips and alpha complices.
Due to computational limitations, an alpha complex could not be calculated for any point clouds with data dimension exceeding 3.
Two notable aspects of Figure \ref{fig:ann} stand out.
First, the alpha complex calculation clearly runs faster than the Vietoris-Rips complex calculation, a trend that becomes clearer as point cloud size increases.
Second, although the Vietoris-Rips complex calculation runtime appears to be independent of underlying data dimension, alpha complex calculation is dependent on it.
Figure \ref{fig:ann} shows a subtle difference between data dimensions 2 and 3 as point cloud size increases.
Although unconcerning for a data dimension up to 3, failure to run any alpha complex calculations with a data dimension of 4 could be cause for concern.
